---
title: "roes - Optical Emission Spectroscopy Data Analysis"
author: "Krunoslav Juraic"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    toc: true
  pdf_document:
    highlight: null
    number_sections: yes
vignette: >
  %\VignetteIndexEntry{Optical Emission Spectroscopy Data Analysis}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
<!---
% rebuild wignete
% rmarkdown::render("vignettes/roes-vignette.Rmd", "all")
% devtools::build_vignette()
% devtools::install()
-->

Roes vignette gives one example of Optical Emission Spectroscopy data analysis. Analysis can be devided in 3 steps:

- OES data import
- OES data cleaning
- OES data comparison with NIST database (spectral lines recognition)

Package can be installed directly from github:
```{r}

```


Before use package should be loaded:
```{r}
library(roes)
```


## Data import
In this example we are using Ocean Optics HR4000 spectrometer and data saved in ASCII files by Oean Optics Spectra Suite spectrometer. There are two Ocean Optics ASCII data files: with header or without header.

## Data cleaning


## NIST spectral lines database



## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
